---
title: "Testing Out with BUCA"
author: "Corrina Kamoroff"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BUCA Data

Testing out R Markdown with BUCA data

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r BUCA}

library(tidyverse)
library(janitor)
library(skimr)
library(httr)
library(readr)
library(lubridate)
library(R2jags)
library(RMark)

toad <- read.csv("/Users/corrinakamoroff/Desktop/BUCA_ Thesis/Project/Working Data/Data_CSV.csv") 

summary(toad)

toad<-toad %>%
  mutate(Date=as.Date(Date, format = "%m/%d/%y")) %>%
  mutate(Year = format(Date, "%Y"))

toad<-clean_names(toad)

toad$'life_stage_sex'[which(toad$'life_stage_sex' == "10")] <- "AM"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "11")] <- "AF"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "12")] <- "E"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "4")] <- "M"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "3")] <- "T"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "8")] <- "J"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "13")] <- "EM"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "9")] <- "AU"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "16")] <- NA


#changing columns-----
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "10")] <- "AM"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "11")] <- "AF"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "12")] <- "E"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "4")] <- "M"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "3")] <- "T"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "8")] <- "J"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "13")] <- "EM"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "9")] <- "AU"
toad$'life_stage_sex'[which(toad$'life_stage_sex' == "16")] <- NA

#More Changes----
toad$svl_mm[which(toad$svl_mm == "999")] <- NA
toad$mass_g[which(toad$mass_g == "999")] <- NA
#Meadow Names-----
toad$`meadow_code`[which(toad$`meadow_code` == "1")] <- "HM"
toad$`meadow_code`[which(toad$`meadow_code` == "2")] <- "CT"
toad$`meadow_code`[which(toad$`meadow_code` == "3")] <- "ST"
toad$`meadow_code`[which(toad$`meadow_code` == "4")] <- "EX"
toad$`meadow_code`[which(toad$`meadow_code` == "5")] <- "BP"
toad$`meadow_code`[which(toad$`meadow_code` == "6")] <- "CM"
toad$`meadow_code`[which(toad$`meadow_code` == "7")] <- "BB"
toad$`meadow_code`[which(toad$`meadow_code` == "8")] <- "WC"
toad$`meadow_code`[which(toad$`meadow_code` == "9")] <- "MM"
toad$`meadow_code`[which(toad$`meadow_code` == "10")] <- "BT"
toad$`meadow_code`[which(toad$`meadow_code` == "11")] <- "RT"
toad$`meadow_code`[which(toad$`meadow_code` == "12")] <- "SN"
toad$`meadow_code`[which(toad$`meadow_code` == "13")] <- "CS"
toad$`meadow_code`[which(toad$`meadow_code` == "14")] <- "GH"
toad$`meadow_code`[which(toad$`meadow_code` == "15")] <- "LT"
toad$`meadow_code`[which(toad$`meadow_code` == "16")] <- "MT"
toad$`meadow_code`[which(toad$`meadow_code` == "17")] <- "MA"
toad$`meadow_code`[which(toad$`meadow_code` == "18")] <- "RP"
toad$`meadow_code`[which(toad$`meadow_code` == "19")] <- "Cl"
toad$`meadow_code`[which(toad$`meadow_code` == "20")] <- "TP"
toad$`meadow_code`[which(toad$`meadow_code` == "21")] <- "TM"
toad$`meadow_code`[which(toad$`meadow_code` == "22")] <- "HL"
toad$`meadow_code`[which(toad$`meadow_code` == "23")] <- "FP"
toad$`meadow_code`[which(toad$`meadow_code` == "25")] <- "SC"

#Change all 999 to NA----
toad$`mark_info_pit_id`[which(toad$`mark_info_pit_id` == "NONE")] <- NA
toad$`mark_info_pit_id`[which(toad$`mark_info_pit_id` == "BLANK")] <- NA
toad$`mark_info_pit_id`[which(toad$`mark_info_pit_id` == 99.0)] <- NA
toad$`mark_info_pit_id`[which(toad$`mark_info_pit_id` == "9.85E+14")] <- NA
toad$`cap_recap`[which(toad$`cap_recap` == "NONE")] <- NA
toad$`cap_recap`[which(toad$`cap_recap` == "BlANK")] <- NA
```

## Plots

```{r pressure, echo=FALSE}
#### GGHightlight--------------------------------
library(gghighlight)

Plot_1<-toad %>% filter(mark_info_pit_id != "") %>%
  ggplot(aes(x=year,y=mass_g,group=mark_info_pit_id, col=life_stage_sex)) +
  geom_point() 

#LifeStage and Sex by time of year (julian day):
toad %>%
  mutate(JDay = format(date,"%j")%>%
           as.numeric()) %>%
  ggplot(aes(x=JDay,y=svl_mm,col=life_stage_sex)) + geom_point(alpha=.6)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
